Fail Faster

### 2025-03-17 paper/paper.tex
more in sig

\begin{lstlisting}
module Bq : sig
  type 'a t
  val return : 'a -> 'a t
  val bind : 'a t -> ('a -> 'b t) -> 'b t
  val gen_int : lo:int -> hi:int -> int t
end
\end{lstlisting}

>>>>

\begin{lstlisting}
module Bq : sig
  type 'a t
  val return : 'a -> 'a t
  val bind : 'a t -> ('a -> 'b t) -> 'b t
  val gen_int : lo:int -> hi:int -> int t

  val weighted_union : (int * 'a t) list -> 'a t

  val size : int t
  val with_size : int -> 'a t -> 'a t

  val fixed_point : ('a t -> 'a t) -> 'a t
  $\dots$
end
\end{lstlisting}
